Dryad Data Package for study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-07-07 dryad/README.Rmd
adding dryad files

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S3.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S4.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S5.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S6.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S7.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S8.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S9.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S10.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S11.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S12.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S13.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S14.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S15.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S16.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from XXX. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S (gray).

>>>>

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S3.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S4.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S5.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Burns et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S6.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Claramunt et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S7.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Gibb et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S8.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S9.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S10.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hooper et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S11.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S12.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S13.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S14.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S15.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Oliveros et al. 2019. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S16.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S17.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S17.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S17 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S18.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S18.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S18 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S19.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S19.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S19 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S20.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Uyeda et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S20.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S20 (gray).
